\documentclass[Report.tex]{subfiles}
\externaldocument[I-]{chapter_1_introduction}
\externaldocument[M-]{chapter_2_method}
\externaldocument[D-]{chapter_3_discardMethod}
\externaldocument[R-]{chapter_4_result}
\externaldocument[RE-]{chapter_6_recognition}

\begin{document}
\chapter{Conclusion}
\label{chap:Conclusion}

\section{Ambition vs reality?}
\begin{flushleft}
Our goals was relatively ambitious compared to the end product. We envisioned
a software which was rotation invariant, light intensity invariant to some
extend; could recognize text with great accuracy. However, it was a far more
challenging task then what we expected. \par
Firstly we started off with an MLP network, which is not the best choice for
image classification. Secondly we didn't have much experience with
machine learning software, so most of our solutions were combinations of
trying to see what worked for others and researching what could give a good result for
our problems. Additionally, as writing everything in the python environment
would be very slow, we decided to write the machine learning algorithms with the
TensorFlow API. This too was a challenge, as it takes some time to understand
how everything in the TensorFlow environment works.
\end{flushleft}

\section{Future work}
Since we divided the problem in 3 parts, we thought of improvments on each part separately.

\subsection{Future Work: Text Segmentation}
On Text Segmentation we would want to be able to detect text in natural images, so a continuation of Stroke Width Transform would be nice.

\subsection{Future Work: Preprocessing}

\subsection{Future Work: Classification}

\section{Final remarks}
Challenge wise, a really great problem, learned a lot about TenserFlow, OpenCV,
CNN, MLP, different datasets avalible open source. \par

Thought the time pressure in the end got us really worked up, without it we doubt
we would of worked as consistently with the project as we did! \par

Considering everything mentioned above, this project was one of the best ``assignments'' we have done at IFI/UNIK.

\begin{itemize}
  \item LeNet vs Our solution
  \item prepo
\end{itemize}

\end{document}
